---
title: "Identifying the role of Wdr37 by position and molecular phenotype of expressing neurons in the mouse brain"
author: "Evgenii O. Tretiakov"
format:
  html:
    toc: true
    df-print: paged
    code-fold: true
    fig-width: 14
    fig-height: 12
    fig-format: retina
    fig-responsive: true
    fig-dpi: 300
execute:
  keep-md: false
  echo: true
  error: false
  message: false
  warning: false
  debug: false
knitr:
  opts_chunk:
    autodep: true
    fig.align: center
    fig.retina: 2
    fig.width: 14
    fig.height: 12
---

```{r setup, include = FALSE}
DOCNAME <- "localisation-of-wdr37"
NOW <- Sys.time()

# Time chunks during knitting
knitr::knit_hooks$set(timeit = function(before) {
  if (before) {
    print(paste("Start:", Sys.time()))
    NOW <<- Sys.time()
  } else {
    print(paste("Stop:", Sys.time()))
    print(Sys.time() - NOW)
  }
})

knitr::knit_hooks$set(debug = function(before, options, envir) {
  if (!before) {
    message(
      paste(names(envir), as.list(envir),
        sep = " = ", collapse = "\n"
      )
    )
  }
})

knitr::opts_chunk$set(
  cache          = FALSE,
  dev            = c("png", "pdf"),
  timeit         = TRUE
)
```

## Load data and setup parameters

```{r libraries, cache=FALSE}
# Load tidyverse infrastructure packages
library(here)
library(tidyverse)
library(RColorBrewer)
library(glmnet)

# Load packages for scRNA-seq analysis and visualisation
library(Seurat)
library(SeuratWrappers)
library(SeuratDisk)
library(scCustomize)
library(swne)
library(ggplot2)
library(cowplot)
library(UpSetR)
library(patchwork)
library(Nebulosa)
library(schex)
```

### Set paths

```{r paths}
set_here()
data_dir <- here("data")
output_dir <- here("outputs")
plots_dir <- here(output_dir, "figures")
tables_dir <- here(output_dir, "tables")
```

### Load helper functions and gene-sets

```{r source, cache = FALSE}
source(here("functions.R"))
source(here("genes.R"))
```

### Set fixed variables

```{r params-computation, cache = FALSE}
# set seed
reseed <- 42
set.seed(seed = reseed)

# available RAM in kB
ram <- check_ram()

# available cores
n.cores <- available_cores(prop2use = .1)

# Parameters for parallel execution
plan("multisession", workers = n.cores)
options(
  future.globals.maxSize = 100000 * 1024^2,
  future.rng.onMisuse = "ignore"
)
plan()
```

## Load data from Zeisel et al. (2018)

```{r load-data, cache = FALSE}
l6.neurons <- Connect(filename = here("l6_r1_neurons.loom"), mode = "r")
l6.neurons
```

```{r init-srt_close-loom}
l6.srt <- as.Seurat(l6.neurons)
l6.neurons$close_all()
```

show srt object
```{r srt}
l6.srt <-
  Store_Palette_Seurat(
    seurat_object = l6.srt,
    palette = rev(brewer.pal(n = 11, name = "Spectral")),
    palette_name = "div_Colour_Pal"
  )

l6.srt
```

show metadata
```{r summary-meta}
skimr::skim(l6.srt@meta.data)
```

Check Violin plots for the expression of the gene of interest (goi) in the different clusters and tissues
```{r plt-goi-vln-cluster, fig.width = 48, fig.height = 6, fig.fullwidth = TRUE}
Idents(l6.srt) <- "ClusterName"
Stacked_VlnPlot(
  seurat_object = l6.srt, features = goi, x_lab_rotate = TRUE,
  color_seed = reseed
)
```

```{r plt-goi-vln-tissue, fig.width = 18, fig.height = 8, fig.fullwidth = TRUE}
Idents(l6.srt) <- "Tissue"
Stacked_VlnPlot(
  seurat_object = l6.srt, features = goi, x_lab_rotate = TRUE,
  color_seed = reseed
)
```

```{r plt-dotplot-goi-by-tissue, fig.width = 48, fig.height = 5, fig.fullwidth = TRUE}
DotPlot_scCustom(
  seurat_object = l6.srt,
  assay = "RNA",
  features = goi,
  flip_axes = TRUE,
  x_lab_rotate = TRUE,
  group.by = "Tissue"
)
```

```{r plt-dotplot-goi-by-cluster, fig.width = 48, fig.height = 5, fig.fullwidth = TRUE}
DotPlot_scCustom(
  seurat_object = l6.srt,
  assay = "RNA",
  features = goi,
  flip_axes = TRUE,
  x_lab_rotate = TRUE,
  group.by = "ClusterName"
)
```

Extact UMAP and tSNE coordinates from the srt object
```{r init-srt-dr}
umap <- l6.srt@meta.data %>%
  select(X_X, X_Y) %>%
  as.matrix()
rownames(umap) <- colnames(l6.srt)
colnames(umap) <- paste0("UMAP_", 1:2)
l6.srt[["umap"]] <- CreateDimReducObject(embeddings = umap, key = "UMAP_", assay = DefaultAssay(l6.srt))

tsne <- l6.srt@meta.data %>%
  select(X_tSNE1, X_tSNE2) %>%
  as.matrix()
rownames(tsne) <- colnames(l6.srt)
colnames(tsne) <- paste0("tSNE_", 1:2)
l6.srt[["tsne"]] <- CreateDimReducObject(embeddings = tsne, key = "tSNE_", assay = DefaultAssay(l6.srt))
```

## Exploratory data analysis
Use standradised pipeline
```{r init-srt-goi}
l6.srt <- NormalizeData(l6.srt)
l6.srt <- FindVariableFeatures(l6.srt, selection.method = "vst", nfeatures = 3500)
l6.srt <- ScaleData(l6.srt)
var.genes <- VariableFeatures(l6.srt)
cell.clusters <- Idents(l6.srt)
```

Check UMAP and tSNE plots for the expression of the gene of interest (goi) in the different clusters and tissues


### tSNE

```{r plt-init-tsne, fig.width = 24, fig.height = 14, fig.fullwidth = TRUE}
DimPlot_scCustom(
  l6.srt,
  reduction = "tsne",
  pt.size = 0.5,
  label = TRUE,
  repel = TRUE,
  figure_plot = TRUE,
  color_seed = reseed
) |
  DimPlot_scCustom(
    l6.srt,
    reduction = "tsne",
    pt.size = 0.5,
    group.by = "ClusterName",
    label = TRUE,
    repel = TRUE,
    figure_plot = TRUE,
    color_seed = reseed
  ) & NoLegend()
```


### UMAP
```{r plt-init-umap, fig.width = 24, fig.height = 14, fig.fullwidth = TRUE}
DimPlot_scCustom(
  l6.srt,
  reduction = "umap",
  pt.size = 0.5,
  label = TRUE,
  repel = TRUE,
  figure_plot = TRUE,
  color_seed = reseed
) |
  DimPlot_scCustom(
    l6.srt,
    reduction = "umap",
    pt.size = 0.5,
    group.by = "ClusterName",
    label = TRUE,
    repel = TRUE,
    figure_plot = TRUE,
    color_seed = reseed
  ) & NoLegend()
```

```{r plt-init-umap-goi, fig.width = 8, fig.height = 36, fig.fullwidth = TRUE}
FeaturePlot_scCustom(l6.srt, goi, num_columns = 1, pt.size = 1, order = T, colors_use = viridis::viridis(n = 100, alpha = .6, direction = -1, option = "E"))
```

```{r plt-init-umap-density-wdr37, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = "Wdr37", custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-pacs1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = "Pacs1", custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = "Pacs2", custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-grm5, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = "Grm5", custom_palette = l6.srt@misc$div_Colour_Pal)
```

### UMAP density plots of interactions between Wdr37 and other features

```{r plt-init-umap-density-wdr37-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Wdr37", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-wdr37-grm5, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Wdr37", "Grm5"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-grm5-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Grm5", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-wdr37-penk, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Wdr37", "Penk"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

### UMAP density plots of neurotransmitter phenotype with Wdr37 and other features

#### GABA

```{r plt-init-umap-density-slc32a1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = c("Slc32a1"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-gad1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = c("Gad1"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-gad2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = c("Gad2"), custom_palette = l6.srt@misc$div_Colour_Pal)
```


#### Glutamate

```{r plt-init-umap-density-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(seurat_object = l6.srt, features = c("Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-wdr37-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Wdr37", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-pacs2-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Pacs2", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

```{r plt-init-umap-density-grm5-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(seurat_object = l6.srt, features = c("Grm5", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal)
```

## Focused data analysis of Wdr37+ brain regions

### Subset CA1 only

```{r subset-srt-goi}
ca1.srt <- subset(l6.srt, idents = "CA1")
ca1.srt <- FindVariableFeatures(ca1.srt, selection.method = "vst", nfeatures = 3500)
ca1.srt <- ScaleData(ca1.srt)
l6.srt <- subset(l6.srt, idents = c("CA1", "Hypoth", "MBd", "MBv", "Medulla", "Pons", "Thal"))
l6.srt <- FindVariableFeatures(l6.srt, selection.method = "vst", nfeatures = 3500)
l6.srt <- ScaleData(l6.srt)
var.genes <- VariableFeatures(l6.srt)
cell.clusters <- Idents(l6.srt)
```

#### Run SWNE for CA1
```{r run-init-swne}
## Run SWNE
l6.srt <- RunSWNE(l6.srt,
  k = 20, genes.embed = goi,
  return.format = "seurat"
)
ca1.srt <- RunSWNE(ca1.srt,
  k = 20, genes.embed = goi,
  return.format = "seurat"
)
```

#### Plot SWNE of CA1

```{r plt-init-swne-ca1}
DimPlot_scCustom(
  ca1.srt,
  reduction = "swne",
  pt.size = 0.5,
  group.by = "ClusterName",
  label = TRUE,
  repel = TRUE,
  figure_plot = TRUE,
  color_seed = reseed
) & NoLegend()
```

#### GABA

```{r plt-ca1-swne-density-slc32a1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(
  seurat_object = ca1.srt,
  features = c("Slc32a1"),
  custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne")
```

```{r plt-ca1-swne-density-gad1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(
  seurat_object = ca1.srt,
  features = c("Gad1"),
  custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne")
```

```{r plt-ca1-swne-density-gad2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(
  seurat_object = ca1.srt,
  features = c("Gad2"),
  custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne")
```


#### Glutamate

```{r plt-ca1-swne-density-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Custom(
  seurat_object = ca1.srt,
  features = c("Slc17a6"),
  custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne")
```

#### SWNE density plots of interactions between Wdr37 and other features

```{r plt-ca1-swne-density-wdr37-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Wdr37", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-ca1-swne-density-wdr37-grm5, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Wdr37", "Grm5"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-ca1-swne-density-grm5-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Grm5", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-ca1-swne-density-wdr37-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Wdr37", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-ca1-swne-density-pacs2-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Pacs2", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-ca1-swne-density-grm5-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = ca1.srt, features = c("Grm5", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

### Plot SWNE of selected regions: CA1, Hypothalamus, Midbrain, Medulla, Pons, Thalamus


```{r plt-init-swne-l6, fig.width = 24, fig.height = 14, fig.fullwidth = TRUE}
DimPlot_scCustom(
  l6.srt,
  reduction = "swne",
  pt.size = 0.5,
  label = TRUE,
  repel = TRUE,
  figure_plot = TRUE,
  color_seed = reseed
) |
  DimPlot_scCustom(
    l6.srt,
    reduction = "swne",
    pt.size = 0.5,
    group.by = "ClusterName",
    label = TRUE,
    repel = TRUE,
    figure_plot = TRUE,
    color_seed = reseed
  ) & NoLegend()
```

### SWNE density plots of interactions between Wdr37 and other features

```{r plt-init-swne-density-wdr37-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Wdr37", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-init-swne-density-wdr37-grm5, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Wdr37", "Grm5"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-init-swne-density-grm5-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Grm5", "Pacs2"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-init-swne-density-wdr37-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Wdr37", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-init-swne-density-pacs2-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Pacs2", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

```{r plt-init-swne-density-grm5-glut, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
Plot_Density_Joint_Only(
  seurat_object = l6.srt, features = c("Grm5", "Slc17a6"), custom_palette = l6.srt@misc$div_Colour_Pal,
  reduction = "swne"
)
```

### Calculate hexagon cell representation to quantify interactions between Wdr37 and other features in the SWNE space
```{r calc-hexagon-representation}
l6.srt <- make_hexbin(l6.srt,
  nbins = 42,
  dimension_reduction = "swne", use_dims = c(1, 2)
)
```


#### Plot hexagon cell representation

```{r plt-hexagon-representation-density, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_density(l6.srt) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-wdr37, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Wdr37",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Wdr37 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-pacs2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Pacs2",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Pacs2 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-grm5, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Grm5",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Grm5 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-slc32a1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Slc32a1",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Slc32a1 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-gad1, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Gad1",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Gad1 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-gad2, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Gad2",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Gad2 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```

```{r plt-hexagon-representation-slc17a6, fig.width = 12, fig.height = 14, fig.fullwidth = TRUE}
plot_hexbin_feature_plus(l6.srt,
  col = "Tissue",
  mod = "RNA", type = "data", feature = "Slc17a6",
  action = "median", xlab = "SWNE1", ylab = "SWNE2",
  title = paste0("Median of mRNA expression of Slc17a6 in logarithmic scale")
) + ggsci::scale_fill_material("amber")
```


#### Quantify and plot hexagon representation of feature interactions with Spearman's correlation

```{r calc-hexagon-representation-spearman-wdr37-pacs2}
plot_hexbin_interact(l6.srt,
  type = c("data", "data"),
  mod = c("RNA", "RNA"), feature = c("Wdr37", "Pacs2"), interact = "corr_spearman",
  ylab = "SWNE2", xlab = "SWNE1",
  title = "Interaction between mRNA expression of Wdr37 and Pacs2/nSpearman rho in hexagonal cells representation"
) +
  scale_fill_gradient2(
    midpoint = 0, space = "Lab",
    low = "navy",
    mid = "wheat1",
    high = "orangered1"
  )
```

```{r calc-hexagon-representation-spearman-wdr37-grm5}
plot_hexbin_interact(l6.srt,
  type = c("data", "data"),
  mod = c("RNA", "RNA"), feature = c("Wdr37", "Grm5"), interact = "corr_spearman",
  ylab = "SWNE2", xlab = "SWNE1",
  title = "Interaction between mRNA expression of Wdr37 and Grm5/nSpearman rho in hexagonal cells representation"
) +
  scale_fill_gradient2(
    midpoint = 0, space = "Lab",
    low = "navy",
    mid = "wheat1",
    high = "orangered1"
  )
```

```{r calc-hexagon-representation-spearman-wdr37-glutamate}
plot_hexbin_interact(l6.srt,
  type = c("data", "data"),
  mod = c("RNA", "RNA"), feature = c("Wdr37", "Slc17a6"), interact = "corr_spearman",
  ylab = "SWNE2", xlab = "SWNE1",
  title = "Interaction between mRNA expression of Wdr37 and Slc17a6/nSpearman rho in hexagonal cells representation"
) +
  scale_fill_gradient2(
    midpoint = 0, space = "Lab",
    low = "navy",
    mid = "wheat1",
    high = "orangered1"
  )
```

```{r calc-hexagon-representation-spearman-pacs2-glutamate}
plot_hexbin_interact(l6.srt,
  type = c("data", "data"),
  mod = c("RNA", "RNA"), feature = c("Pacs2", "Slc17a6"), interact = "corr_spearman",
  ylab = "SWNE2", xlab = "SWNE1",
  title = "Interaction between mRNA expression of Pacs2 and Slc17a6/nSpearman rho in hexagonal cells representation"
) +
  scale_fill_gradient2(
    midpoint = 0, space = "Lab",
    low = "navy",
    mid = "wheat1",
    high = "orangered1"
  )
```

```{r calc-hexagon-representation-spearman-grm5-glutamate}
plot_hexbin_interact(l6.srt,
  type = c("data", "data"),
  mod = c("RNA", "RNA"), feature = c("Grm5", "Slc17a6"), interact = "corr_spearman",
  ylab = "SWNE2", xlab = "SWNE1",
  title = "Interaction between mRNA expression of Grm5 and Slc17a6/nSpearman rho in hexagonal cells representation"
) +
  scale_fill_gradient2(
    midpoint = 0, space = "Lab",
    low = "navy",
    mid = "wheat1",
    high = "orangered1"
  )
```

### Save results
```{r save-results}
write_rds(l6.srt, file = here("l6.srt.rds"))
```

```{r session-info}
sessioninfo::session_info()
```
